Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-12 manuscript/analysis.tex
Complete implementation section.

\begin{figure}[ht]
\centering
\includegraphics[width=\columnwidth]{figures/sampleLifeHistory.png}
\caption{A single run of the simulation, with $\lambda$=2. Each of 50 nodes is
given an initial wealth of 50 units, a regular income distributed as
$\sim\mathcal{N}(20,5)$, a metabolic rate of 5, and a proto threshold of 65.}
\label{fig:singleRun}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=\columnwidth]{figures/sampleLifeHistory.png}
\caption{A single run of the simulation, with $\lambda$=2. Each of 50 nodes is
given an initial wealth of $\sim\mathcal{U}(0,50)$ units, a regular income
distributed as $\sim\mathcal{N}(20,5)$, a metabolic rate of 5, and a proto
threshold of 65.} \label{fig:singleRun}
\end{figure}
